
\documentclass[aspectratio=1610]{beamer}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{hyperref} % before url package otherwise there is a pb
\usepackage{url}
\usepackage[normalem]{ulem}

\setbeamertemplate{navigation symbols}{%
    \usebeamerfont{footline}%
    \usebeamercolor[fg]{footline}%
    \hspace{1em}%
    \insertframenumber/\inserttotalframenumber
}
\setbeamercolor{footline}{fg=black}

\usepackage{tikz}
\usetikzlibrary{calc, positioning, arrows.meta}
\usetikzlibrary{shapes.geometric} % for ellipse
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\tikzset{
  state/.style={
    rectangle,
    rounded corners,
    draw=black, thick,
    minimum height=2em,
    inner sep=2pt,
    text centered,
  },
}
\usetikzlibrary{tikzmark}
\usepackage{pgfplots}

\usepackage{multirow}
\usepackage{multicol}

\begin{document}

\begin{frame}{NIST candidates (pros and cons)}
  Standardization since 2016... and \xout{the winner is} the winners are:
  \begin{itemize}
    \item \textbf{Dilithium -- ML-DSA}, based on lattices,
    \item \textbf{Falcon -- FN-DSA}, based on lattices,
    \item SPHINCS -- SLH-DSA, based on hash functions (big and expensive)
  \end{itemize}

  How to choose?\pause
  \begin{center}
    \begin{tabular}{|l|c|c|}
      \hline
      & \textbf{ML-DSA} & \textbf{FN-DSA}\\
      \hline
      \textbf{EIP} &  \href{
        https://github.com/ethereum/EIPs/blob/master/EIPS/eip-8051.md
      }{
        \textcolor{blue}{8051}
        } &
        \href{
        https://github.com/ethereum/EIPs/blob/master/EIPS/eip-8052.md
      }{
        \textcolor{blue}{8052}
        } \\
      \hline
      \textbf{Public key} & \textcolor{orange}{1312B} & \textcolor{green}{897B} \\
      \textbf{Signature}  & \textcolor{orange}{2420B} & \textcolor{green}{666B} \\
      \hline
      \textbf{On-chain cost} &\textcolor{orange}{13.0M gas} {\tiny (8.3M gas)} &\textcolor{orange}{4.1M gas} {\tiny (1.6M gas)}\\
      \hline
      \textbf{Standardized?}  &        \textcolor{green}{FIPS 204} &   \textcolor{red}{not yet} (since 2 years) \\
      \textbf{Signer implementation} & \textcolor{green}{Easy, many} & Tricky, floating point\\
      \textbf{Hardware integration} &  \textcolor{green}{Done} &       High RAM requirements\\
      \textbf{Industrial integration} & Passkey, Apple (soon) & no\\
      \hline
      \textbf{ZK variant} & Possible & \textcolor{red}{Overstretch attacks}\\
      \hline
    \end{tabular}
  \end{center}
\end{frame}

\begin{frame}{EIPs 8051 and 8052}
  \begin{itemize}
    \item \textbf{EIP 8051}: \href{
        https://github.com/ethereum/EIPs/blob/master/EIPS/eip-8051.md
      }{
        \textcolor{blue}{link}
        }
    \begin{itemize}
      \item Two precompiles:
      \begin{itemize}
        \item MLDSA: NIST-compliant with SHAKE256\\
        (verification: 13.0 M gas, not far from the tx limit of 16M!).
        \item MLDSA-ETH: replacement with a counter-mode Keccak PRNG\\
        (verification: 8.3M gas).
      \end{itemize}
      \item Test vector provided (generated from NIST reference implementation).
      \item Integrated into a 4337 hybrid (MLDSA + ECDSA) account:\\
      Try it by yourself!
    \end{itemize}
    \pause
    \item \textbf{EIP 8052}: \href{
        https://github.com/ethereum/EIPs/blob/master/EIPS/eip-8052.md
      }{
        \textcolor{blue}{link}
        }
    \begin{itemize}
      \item Separation of the hash part and the polynomial arithmetic: 
      \begin{itemize}
        \item FALCON: NIST-compliant with SHAKE256\\
        (verification: 4.1M gas).
        \item ETH-FALCON: replacement with a counter-mode Keccak PRNG\\
        (verification: 1.6M gas).
      \end{itemize}
      \item Precompiles for FALCON-CORE and HASH-TO-POINT (one for Shake256, one for KeccakPRNGone).
      \item Test vector provided (generated from NIST reference implementation).
      \item Integration in a 4337 account in progress...
    \end{itemize}
  \end{itemize}
\end{frame}



\end{document}
